A higher order approximate static condensation method for multi-material diffusion problems

### 2018-11-27 num_sec.tex
Fix directory path for images

	\begin{figure}[h]
		\centering
		\begin{subfigure}{.3\linewidth}
			\centering
			\includegraphicsw{transient2/movie_frames/ref/frame_1s34.png}
			\caption{Reference}
		\end{subfigure}%
		\hfill
		\begin{subfigure}{.3\linewidth}
			\centering
			\includegraphicsw{transient2.1/movie_frames/arithmetic_homo/frame_1s43.png}
			\caption{Arithmetic homo.}	
		\end{subfigure}%
		\hfill
		\begin{subfigure}{.3\linewidth}
			\centering
			\includegraphicsw{transient2.1/movie_frames/harmonic_homo/frame_1s43.png}
			\caption{Harmonic homo.}	
		\end{subfigure}%
		\par
		\begin{subfigure}{.3\linewidth}
			\centering
			\includegraphicsw{transient2.1/movie_frames/asc0/frame_1s43.png}
			\caption{ASC(0)}
		\end{subfigure}%
		\hfill
		\begin{subfigure}{.3\linewidth}
			\centering
			\includegraphicsw{transient2.1/movie_frames/asc1/frame_1s43.png}
			\caption{ASC(1)}	
		\end{subfigure}%
		\hfill
		\begin{subfigure}{.3\linewidth}
			\centering
			\includegraphicsw{transient2.1/movie_frames/asc_diff/frame_1s43.png}
			\caption{ASC(0,\,1) difference}	
		\end{subfigure}%
\caption{Comparison of the discrete solutions~$p_h$ for~$h = 1.5 \times 10^{-1}$, $t = 1.25$. \label{fig:transient:comp}}
	\end{figure}

	%% \begin{figure}[h]
	%% 	\centering
	%% 	\begin{subfigure}{.45\linewidth}
	%% 		\centering
	%% 		\includegraphicsw{transient2.1/movie_slices_frames/frame_0s25.png}
	%% 		\caption{Coarse mesh, $t = 0.25$}
	%% 	\end{subfigure}%
	%% 	\hfill
	%% 	\begin{subfigure}{.45\linewidth}
	%% 		\centering
	%% 		\includegraphicsw{transient2.1/movie_slices_frames/frame_1s50.png}
	%% 		\caption{Coarse mesh, $t = 1.50$}	
	%% 	\end{subfigure}%
	%% 	\par
	%% 	\begin{subfigure}{.45\linewidth}
	%% 		\centering
	%% 		\includegraphicsw{transient2/movie_slices_frames/frame_0s25.png}
	%% 		\caption{Fine mesh, $t = 0.25$}
	%% 	\end{subfigure}%
	%% 	\hfill
	%% 	\begin{subfigure}{.45\linewidth}
	%% 		\centering
	%% 		\includegraphicsw{transient2/movie_slices_frames/frame_1s50.png}
	%% 		\caption{Fine mesh, $t = 1.50$}	
	%% 	\end{subfigure}%
	%% 	\caption{Comparison of the cuts~$p_h((x,0.5), t)$ of discrete solutions for coarse and fine meshes, $h = 1.5 \times 10^{-1}$ and $h = 8.1 \times 10^{-2}$. 		\label{fig:transient:cuts}}
	%% \end{figure}

	\begin{figure}[h]
		\centering
		\begin{subfigure}{.8\linewidth}
			\centering
			\includegraphicsw{transient2.1/l2err.png}
			\caption{Coarse mesh}
		\end{subfigure}%
		\par
		\begin{subfigure}{.8\linewidth}
			\centering
			\includegraphicsw{transient2/l2err.png}
			\caption{Fine mesh}	
		\end{subfigure}%
		\caption{$\lTwo$-norm of the error computed for the inclusion~$\Omega_2 \cup \Omega_3$ for coarse and fine meshes, $h = 1.5 \times 10^{-1}$ and $h = 8.1 \times 10^{-2}$. \label{fig:transient:err}}
	\end{figure}

>>>>

	\begin{figure}[h]
		\centering
		\begin{subfigure}{.3\linewidth}
			\centering
			\includegraphicsw{transient2/movie_frames/ref/frame_1s34.png}
			\caption{Reference}
		\end{subfigure}%
		\hfill
		\begin{subfigure}{.3\linewidth}
			\centering
			\includegraphicsw{transient2-1/movie_frames/arithmetic_homo/frame_1s43.png}
			\caption{Arithmetic homo.}	
		\end{subfigure}%
		\hfill
		\begin{subfigure}{.3\linewidth}
			\centering
			\includegraphicsw{transient2-1/movie_frames/harmonic_homo/frame_1s43.png}
			\caption{Harmonic homo.}	
		\end{subfigure}%
		\par
		\begin{subfigure}{.3\linewidth}
			\centering
			\includegraphicsw{transient2-1/movie_frames/asc0/frame_1s43.png}
			\caption{ASC(0)}
		\end{subfigure}%
		\hfill
		\begin{subfigure}{.3\linewidth}
			\centering
			\includegraphicsw{transient2-1/movie_frames/asc1/frame_1s43.png}
			\caption{ASC(1)}	
		\end{subfigure}%
		\hfill
		\begin{subfigure}{.3\linewidth}
			\centering
			\includegraphicsw{transient2-1/movie_frames/asc_diff/frame_1s43.png}
			\caption{ASC(0,\,1) difference}	
		\end{subfigure}%
\caption{Comparison of the discrete solutions~$p_h$ for~$h = 1.5 \times 10^{-1}$, $t = 1.25$. \label{fig:transient:comp}}
	\end{figure}

	%% \begin{figure}[h]
	%% 	\centering
	%% 	\begin{subfigure}{.45\linewidth}
	%% 		\centering
	%% 		\includegraphicsw{transient2-1/movie_slices_frames/frame_0s25.png}
	%% 		\caption{Coarse mesh, $t = 0.25$}
	%% 	\end{subfigure}%
	%% 	\hfill
	%% 	\begin{subfigure}{.45\linewidth}
	%% 		\centering
	%% 		\includegraphicsw{transient2-1/movie_slices_frames/frame_1s50.png}
	%% 		\caption{Coarse mesh, $t = 1.50$}	
	%% 	\end{subfigure}%
	%% 	\par
	%% 	\begin{subfigure}{.45\linewidth}
	%% 		\centering
	%% 		\includegraphicsw{transient2/movie_slices_frames/frame_0s25.png}
	%% 		\caption{Fine mesh, $t = 0.25$}
	%% 	\end{subfigure}%
	%% 	\hfill
	%% 	\begin{subfigure}{.45\linewidth}
	%% 		\centering
	%% 		\includegraphicsw{transient2/movie_slices_frames/frame_1s50.png}
	%% 		\caption{Fine mesh, $t = 1.50$}	
	%% 	\end{subfigure}%
	%% 	\caption{Comparison of the cuts~$p_h((x,0.5), t)$ of discrete solutions for coarse and fine meshes, $h = 1.5 \times 10^{-1}$ and $h = 8.1 \times 10^{-2}$. 		\label{fig:transient:cuts}}
	%% \end{figure}

	\begin{figure}[h]
		\centering
		\begin{subfigure}{.8\linewidth}
			\centering
			\includegraphicsw{transient2-1/l2err.png}
			\caption{Coarse mesh}
		\end{subfigure}%
		\par
		\begin{subfigure}{.8\linewidth}
			\centering
			\includegraphicsw{transient2/l2err.png}
			\caption{Fine mesh}	
		\end{subfigure}%
		\caption{$\lTwo$-norm of the error computed for the inclusion~$\Omega_2 \cup \Omega_3$ for coarse and fine meshes, $h = 1.5 \times 10^{-1}$ and $h = 8.1 \times 10^{-2}$. \label{fig:transient:err}}
	\end{figure}
